\thetitle

### 2020-11-09 sun_phases/spin_qudit_tomo.tex
change some defaults in error bound runtime scripts

Computing $\S_V^2$ to certify the bound in Eq.~\eqref{eq:bound_eps} requires constructing the measurement matrix $M_V$ and finding its singular values.
This complexity of this task can be greatly reduced by the fact that the degree $\ell$ of the transition operator $T_{\ell,0}$ is preserved under rotations, which implies that the unitary
\begin{align}
  U \equiv \sum_{\ell,m} \ket{\ell m} \obra{T_{\ell m}},
\end{align}
block-diagonalizes the measurement matrix:
\begin{align}
  U M_V = \sum_\ell \op{\ell} \otimes M_{V\ell},
\end{align}
where the $\p{2\ell+1}\times\abs{V}$ blocks are
\begin{align}
  M_{V\ell} \equiv \sum_{m,\v v} \ket{m} \obk{T_{\ell m}|T_{\v v\ell,0}} \bra{\v v}
  = \sum_{m,\v v} D^\ell_{m,0}\p{\v v} \op{m}{\v v}.
\end{align}
As the singular values of $M_V$ are invariant under unitary transformations, it follows that
\begin{align}
  \S_V^2 = \sum_\ell \S_{V\ell}^2,
  &&
  \S_{V\ell}^2 \equiv \norm{M_{V\ell}^{-1}}^2,
\end{align}
where $M_{V\ell}^{-1}$ is the right inverse of $M_{V\ell}$.
Constructing the block $M_{V\ell}$ and computing its singular values takes at most $O(\abs{V}d^2)$ time (see Appendix \ref{sec:compute} for additional details on efficiently computing $\S_{V\ell}^2$ [\red{todo: write tutorial}]).
Altogether, if we assume that $\abs{V}\sim d$, then computing $\S_V^2$ to certify the bound in Eq.~\eqref{eq:bound_eps} takes $O(d^4)$ serial or $O(d^3)$ parallel runtime (see Figure \ref{fig:times}).

>>>>

Computing $\S_V^2$ to certify the bound in Eq.~\eqref{eq:bound_eps} requires constructing the measurement matrix $M_V$ and finding its singular values.
The complexity of this task can be greatly reduced by the fact that the degree $\ell$ of the transition operator $T_{\ell,0}$ is preserved under rotations, which implies that the unitary
\begin{align}
  U \equiv \sum_{\ell,m} \ket{\ell m} \obra{T_{\ell m}},
\end{align}
block-diagonalizes the measurement matrix:
\begin{align}
  U M_V = \sum_\ell \op{\ell} \otimes M_{V\ell},
\end{align}
where the $\p{2\ell+1}\times\abs{V}$ blocks are
\begin{align}
  M_{V\ell} \equiv \sum_{m,\v v} \ket{m} \obk{T_{\ell m}|T_{\v v\ell,0}} \bra{\v v}
  = \sum_{m,\v v} D^\ell_{m,0}\p{\v v} \op{m}{\v v}.
\end{align}
As the singular values of $M_V$ are invariant under unitary transformations, it follows that
\begin{align}
  \S_V^2 = \sum_\ell \S_{V\ell}^2,
  &&
  \S_{V\ell}^2 \equiv \norm{M_{V\ell}^{-1}}^2,
\end{align}
where $M_{V\ell}^{-1}$ is the right inverse of $M_{V\ell}$.
Constructing the block $M_{V\ell}$ and computing its singular values takes at most $O(\abs{V}d^2)$ time (see Appendix \ref{sec:compute} for additional details on efficiently computing $\S_{V\ell}^2$ [\red{todo: write tutorial}]).
Altogether, if we assume that $\abs{V}\sim d$, then computing $\S_V^2$ to certify the bound in Eq.~\eqref{eq:bound_eps} takes $O(d^4)$ serial or $O(d^3)$ parallel runtime (see Figure \ref{fig:times}).
